---
title: "results"
author: "Anton Hung"
date: "2024-10-07"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(dplyr)
library(ggplot2)
```


# Function for generating data

```{r}
generate_data <- function(n) {
  W1 <- runif(n, 0, 2)
  W2_4 <- matrix(rbinom(n * 3, 1, 0.5), ncol = 3)
  colnames(W2_4) <- paste0("W", 2:4)
  W <- cbind(data.frame(W1 = W1), W2_4)
  A <- g(W)
  # A <- sample(c(0, 1), size = n, replace = TRUE)
  Y <- Q(cbind(W,A))
  cbind(W, data.frame(A = A), data.frame(Y = Y))
}

g <- function(W) {
  p <- with(W, plogis(W1 + W2*W3 - 2*W4))
  rbinom(nrow(W), 1, p)
}

Q <- function(W_A) {
  # expit(W1 + W2xW3 + W4xA - 3)
  p <- with(W_A, plogis(W1 + W2*W3 - 3))
  rbinom(nrow(W_A), 1, p)
}
```

### Comparison of Y1 vs Y0

For each of the 1000 datasets, we can compute the sample mean Y1 and sample mean Y0. If the ATE was truly 0, then we should see an approximately 50:50 ratio for which one is larger between Y1 and Y0. 

Instead, we see and approximately 85:15 ratio in favour of Y1.

```{r}
result <- numeric(1000)
for (i in 1:1000) {
  set.seed(i)
  data <- generate_data(200)
  result[i] <- mean(data[which(data$A==0),"Y"]) > mean(data[which(data$A==1),"Y"])
}
table(result)
```

#### Used TML3 to generate estimates ...


# Recreating Figure 1 from the paper

```{r}
results <- rbind(readRDS("/Users/anton/Library/CloudStorage/OneDrive-ColumbiaUniversityIrvingMedicalCenter/Q3_2024/random-seed-effects/fig_1_results/seeds-1-1000_sensitivity.rds"))

results <- results |> 
  mutate(ATE = A1_estimate - A0_estimate,
         ATE_low = ATE - 1.96*sqrt(A0_se^2 + A1_se^2),
         ATE_high = ATE + 1.96*sqrt(A0_se^2 + A1_se^2),
         CI_width = ATE_high-ATE_low)

results <- results |>
  arrange(ATE_low) |>
  mutate(rank = row_number())

ggplot(results, aes(x = rank, y = ATE)) +
  geom_errorbar(aes(ymin = ATE_low, ymax = ATE_high, color=ATE_low<0)) +
  geom_point() + 
  ylim(-0.5, 0.5) +
  geom_hline(yintercept = 0, linetype = "dashed")
```

### Some CIs are extremely wide...

```{r}
ggplot(results, aes(x = rank, y = ATE)) +
  geom_errorbar(aes(ymin = ATE_low, ymax = ATE_high, color=ATE_low<0)) +
  geom_point() + 
  # ylim(-0.5, 0.5) +
  geom_hline(yintercept = 0, linetype = "dashed")
```

### Proportion of Confidence Intervals that do not overlap with 0

1.1%, and all non-overlapping CIs lie above 0.

```{r}
table(results$ATE_low > 0)
table(results$ATE_high < 0)
```


### How many ATE values are above 0?

60:40 ratio? Not 50:50 as would be expected under the null, or even 85:15 as we saw when comparing the true sample means.

```{r}
table(results$ATE > 0)
```

